%-------------------------
% Resume in Latex
% Author : Kevin Antony
% Based off of: https://github.com/jakegut/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Kevin Antony} \\ \vspace{1pt}
    \small +91-7559044582 $|$ \href{mailto:kevina.cs.20@nitj.ac.in}{\underline{kevina.cs.20@nitj.ac.in}} $|$ 
    \href{https://linkedin.com/in/kevin-antony}{\underline{linkedin.com/in/kevin-antony}} $|$
    \href{https://github.com/kevnantony}{\underline{github.com/kevnantony}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dr. B R Ambedkar National Institute of Technology, Jalandhar}{Punjab, India}
      {Bachelor of Technology in Computer Science \& Engineering, \emph{CGPA: 7.5/10}}{Dec. 2020 -- May 2024}
    \resumeSubheading
      {Indian School Al Ghubra}{Muscat, Oman}
      {Central Board Of Secondary Education, \emph{Class X: 87\%, Class XII: 90\%} }{May 2018 -- May 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern (Founder's Office)- ML \& AI }{June 2023 -- July 2023}
      {AnCrypto}{Chandigarh, India}
      \resumeItemListStart
        \resumeItem{Developed a Generative AI assistant, used LangChain for proficient multi-document retrieval and question-answering.}
        \resumeItem{Integrated Chroma vector store, OpenAI embeddings, and employed the GPT-3.5-turbo language model to optimize document indexing, enhance similarity matching, and ensure seamless database persistence.}
        \resumeItem{Engineered a Time-Series forecasting toolkit, bringing together an ensemble of LSTM, XGBoost, ARIMA, and Prophet models.}
        \resumeItem{Utilized these models to forecast future prices of multiple cryptocurrencies, enhancing strategic decision-making and market analysis.}

      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Vice President}{May 2023 -- Present}
      {Entrepreneurship Cell, NIT Jalandhar}{Punjab, India}
      \resumeItemListStart
        \resumeItem{Led a dynamic team of 25 members, fostering collaboration, motivation, and goal alignment.}
        \resumeItem{Directed end-to-end event planning, encompassing concept ideation, logistics, marketing, and post-event evaluations.}
        \resumeItem{Fostered strategic alliances with prominent industry professionals, facilitating guest lectures and workshops, benefitting 300+ attendees.}
    \resumeItemListEnd

    \resumeSubheading
      {Product Intern}{Feb. 2023 -- Present}
      {Deep Connection}{Remote}
      \resumeItemListStart
        \resumeItem{Executed thorough market research to assess product-market fit (PMF), incorporating user needs and industry trends.}
        \resumeItem{Collaborated closely with designers and developers to implement user-driven design improvements.}
        \resumeItem{Played a pivotal role in the building of an AI tool within the app, involving coding, testing, and iterative refinement.}
        \resumeItem{Formulated a strategic plan for gamifying the app to increase user engagement and retention.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Jwala}}{June 2022 -- May. 2023}
          \resumeItemListStart
            \resumeItem{Developed a fire detection system that utilized YOLOv5 for fire & smoke detection. The system has a detection accuracy of 70.7\% and an inaccuracy of 15.3\%. }
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Dyslexic Handwriting Detector} }{Aug. 2021 -- Apr. 2022}
          \resumeItemListStart
            \resumeItem{Engineered a Convolutional Neural Network From Scratch trained to identify handwriting of individuals with special needs mainly targeting dysgraphia.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Audio Spectrum Analyser} }{May 2020 -- May 2021}
          \resumeItemListStart
            \resumeItem{Built a series of Jupyter notebooks and python files which stream audio from a microphone using pyaudio and displays the waveform with matplotlib for data visualization.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, SQL (Postgres), R} \\
     \textbf{Developer Tools}{: Git, Docker, Google Cloud Platform, VS Code, Visual Studio, PyCharm, Eclipse} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, Tensorflow, Keras, Pytorch, SciPy}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}


